FoRTE baseline

### 2019-06-05 analysis/paper/paper.Rmd
Add paragraph introducing uncertainty

Temperate forests in the Upper Midwest are important.
{C sequestration}.
{Other ecosystem services}.
However, the fate of these forests is highly uncertain.
The natural ecological succession of these forests has been significantly altered by the interactions of a significantly different and rapidly changing climate, and novel disturbance regimes under which some natural disturbances (e.g. fire) are suppressed while others (e.g. harvest; pests and pathogens) may be becoming more frequent. <!-- TODO refs -->
Therefore, predictions about the future of these forests based on past analogs may not be reliable.

@@

A key challenge of vegetation modeling research over the last several decades has been the development of approaches that capture the emergent biogeochemical and ecological outcomes of interactions between individual plants without the need for explicitly simulating each individual [@purves_2008_predictive].
One such approach is the "ecosystem demography" approach, which uses a system of partial differential equations to simulate the emergent mean behavior of "cohorts" of individuals of similar composition, size, and age [@moorcroft_2001_method]. <!-- TODO Run this description by Mike? -->
The original "Ecosystem Demography" (ED) model [@moorcroft_2001_method] was enhanced by @medvigy_2009_mechanistic (as ED2) with fully-coupled leaf physiology, canopy radiative transfer, and micrometeorology, and each of these components have been further refined over the last decade [culminating in ED2.2; @longo_2019_ed1].
Various versions of the ED model have been validated in boreal [@medvigy_2011_predicting], temperate [@medvigy_2009_mechanistic; @dietze_2014_quantitative; @raczka_2018_what], and tropical biomes [@moorcroft_2001_method; @longo_2019_ed2], and have been applied in:
- paleoecological studies [@rollinson_2017_emergent];
- free-air CO~2~ enrichment studies [@dekauwe_2013_forest; @miller_2015_alteration];
- estimation of potential carbon stocks [@hurtt_2004_beyond_potential_vegetation]

>>>>

Temperate forests in the Upper Midwest are important.
{C sequestration}.
{Other ecosystem services}.
However, the fate of these forests is highly uncertain.
The natural ecological succession of these forests has been significantly altered by the interactions of a significantly different and rapidly changing climate, and novel disturbance regimes under which some natural disturbances (e.g. fire) are suppressed while others (e.g. harvest; pests and pathogens) may be becoming more frequent. <!-- TODO refs -->
{UMBS ecological background/natural history?} 
Therefore, predictions about the future of these forests based on past analogs may not be reliable.

@@

A key challenge of vegetation modeling research over the last several decades has been the development of approaches that capture the emergent biogeochemical and ecological outcomes of interactions between individual plants without the need for explicitly simulating each individual [@purves_2008_predictive].
One such approach is the "ecosystem demography" approach, which uses a system of partial differential equations to simulate the emergent mean behavior of "cohorts" of individuals of similar composition, size, and age [@moorcroft_2001_method]. <!-- TODO Run this description by Mike? -->
The original "Ecosystem Demography" (ED) model [@moorcroft_2001_method] was enhanced by @medvigy_2009_mechanistic (as ED2) with fully-coupled leaf physiology, canopy radiative transfer, and micrometeorology, and each of these components have been further refined over the last decade [culminating in ED2.2; @longo_2019_ed1].
Various versions of the ED model have been validated in boreal [@medvigy_2011_predicting], temperate [@medvigy_2009_mechanistic; @dietze_2014_quantitative; @raczka_2018_what], and tropical biomes [@moorcroft_2001_method; @longo_2019_ed2], and have been applied in:
- paleoecological studies [@rollinson_2017_emergent];
- free-air CO~2~ enrichment studies [@dekauwe_2013_forest; @miller_2015_alteration];
- estimation of potential carbon stocks [@hurtt_2004_beyond_potential_vegetation]
- vegetation-climate feedbacks {Swann, etc} <!-- TODO -->

Vegetation model projections are inherently uncertain, and this uncertainty stems from several sources.
_Driver_ uncertainty refers to uncertainty in data about processes that are essential to the system in question but are not represented by the model (e.g. weather and climate for vegetation models).
_Initial condition_ uncertainty arises from the fact that models have to start somewhere, and the exact conditions at the place and time simulations begin are uncertain.
_Process_ or _structural_ uncertainty arises because vegetation models necessarily only represent a subset of all processes involved in plant biology, and that the process that are included can usually be represented in multiple different ways.
Finally, _parameter_ uncertainty arises because of natural variability and imperfect calibration of the above process representations.
The focus of this study is on the interaction between parametric and structural uncertainty; driver uncertainty is outside the scope of this study, and initial condition uncertainty is minimized by our experimental design, which is conditioned on a specific initial condition (near bare ground).
<!-- TODO This whole paragraph is awkward -->
